si: code and prose exploring Spatial Interaction models

### 2022-04-22 README.qmd
Update with logz map
Former-commit-id: 6a9eac73e9a4846114354f8c2020aced72cea4ff

@@

```{r}
od_res = od %>% 
  si_calculate(fun = gravity_model, 
               m = origin_all,
               n = destination_all,
               d = distance_euclidean,
               beta = 0.3)
od_res %>% 
  select(interaction) %>% 
  plot()
```

What just happened?
As the example above shows, the package allows/encourages you to define and use your own functions to estimate the amount of interaction/movement between places.
The resulting estimates of interaction, returned in the column `res` and plotted with distance in the graphic above, resulted from our choice of spatial interaction model inputs, allowing a wide range of alternative approaches to be implemented.
This flexibility is a key aspect of the package, enabling small and easily modified functions to be implemented and tested.

>>>>

What just happened?
We created an 'OD data frame' from geographic origins and destinations, and then estimated a simple gravity model based on the population in origin and destination zones and a custom distance decay function.
As the example above shows, the package allows/encourages you to define and use your own functions to estimate the amount of interaction/movement between places.

@@

```{r}
od_res = od %>% 
  si_calculate(fun = gravity_model, 
               m = origin_all,
               n = destination_all,
               d = distance_euclidean,
               beta = 0.3)
od_res %>% 
  select(interaction)
```

The resulting estimates of interaction, returned in the column `interaction` and plotted with distance in the graphic above, resulted from our choice of spatial interaction model inputs, allowing a wide range of alternative approaches to be implemented.
This flexibility is a key aspect of the package, enabling small and easily modified functions to be implemented and tested.
